Source Code of Test Cases for Iterative Deepening

### 2015-11-18 pldi-16/design.tex
implement brandon's comments, and trim a bit; back onto 12th page, oops

\newcommand\AllJobs{\ensuremath{\mathcal{J}}}
\begin{algorithm}[t]
	\SetKwInOut{Input}{Input}
	\Input{$j_0$, the currently-running job}
	\Input{\AllJobs, the set of all existing jobs}
	\Input{$\alpha$, an instruction reported by the MC as part of a racing access pair}
	\If{$\forall j \in \AllJobs,$
	\GetPPSet{$j_0$} $\cup$ $\alpha$
	$\not\subseteq$
	\GetPPSet{$j$}
	}{
		AddNewJob(\GetPPSet{$j_0$} $\cup$ $\alpha$, HeuristicPriority($\alpha$))
	}
	\caption{Adding new jobs with data-race PPs.}
	\label{alg:handledatarace}
\end{algorithm}

@@

Furthermore, we do not always strictly increase the number of PPs when we find a new data race.
%When \quicksand~receives a data race report, it adds two new jobs to its workqueue:
For each instruction involved in a data race, \quicksand~adds two new jobs:
a ``small'' job to preempt on that instruction only,
and a ``big'' job to preempt on that instruction as well as each PP used by the reporting job.
%
Hence,
%together with the logic in \sect{\ref{sec:classifying}},
each {\em pair} of racing accesses will spawn four new jobs, as shown in Figure~\ref{fig:new-dr-jobs}.
%
The rationale of spawning multiple jobs is that which will be more fruitful cannot be known in advance:
while the big job risks not completing in time,
the small job risks missing the data race entirely if the original PPs were required to expose it.
% TODO CAMREADY: Put numbers here.
In practice, we observed some bugs found quickly by these small jobs, and other bugs missed by the small jobs found eventually by the big jobs,
which motivates the need for Iterative Deepening to prioritize the jobs at runtime.

@@

The new spaces may expose a failure, in which case we report a data-race bug,
or complete successfully, which indicates a benign or false-positive data race.
They may also uncover a new data-race candidate entirely, %in some alternate interleaving,
in which case we iteratively advance to a superset state space containing PPs for both racing access pairs.
%Because Iterative Deepening is
Being constrained by a CPU budget,
we may time out before completing a data race's associated state space,
in which case it remains a potential false positive that the user must handle.

>>>>

\newcommand\AllJobs{\ensuremath{\mathcal{J}}}
\begin{algorithm}[t]
	\SetKwInOut{Input}{Input}
	\Input{$j_0$, the currently-running job}
	\Input{\AllJobs, the set of all existing jobs}
	\Input{$\alpha$, an instruction reported by the MC as part of a racing access pair}
	\If{$\forall j \in \AllJobs,$
	\GetPPSet{$j_0$} $\cup$ $\alpha$
	$\not\subseteq$
	\GetPPSet{$j$}
	}{
		AddNewJob(\GetPPSet{$j_0$} $\cup$ $\alpha$, HeuristicPriority($\alpha$)) \\
	}
	\If{$\forall j \in \AllJobs,$ \GetPPSet{$j$} $\neq \{\alpha\}$}{
		AddNewJob($\{\alpha\}$, HeuristicPriority($\alpha$))
	}
	\caption{Adding new jobs with data-race PPs.}
	\label{alg:handledatarace}
\end{algorithm}

@@

Furthermore, we do not always strictly increase the number of PPs when we find a new data race.
%When \quicksand~receives a data race report, it adds two new jobs to its workqueue:
For each instruction involved in a data race, \quicksand~adds two new jobs:
a ``small'' job to preempt on that instruction only (line 5),
and a ``big'' job to preempt on that instruction as well as each PP used by the reporting job (line 2).
%
Hence,
%together with the logic in \sect{\ref{sec:classifying}},
each {\em pair} of racing accesses will spawn four new jobs, as shown in Figure~\ref{fig:new-dr-jobs}.
%
The rationale of spawning multiple jobs is that which will be more fruitful cannot be known in advance:
while the big job risks not completing in time,
the small job risks missing the data race entirely if the original PPs were required to expose it.
% TODO CAMREADY: Put numbers here.
In practice, we observed some bugs found quickly by these small jobs, and other bugs missed by the small jobs found eventually by the big jobs,
which motivates the need for Iterative Deepening to prioritize the jobs at runtime.

@@

The new state spaces may expose a failure, in which case we report a data-race bug,
or complete successfully, which indicates a benign or false-positive data race.
They may also uncover a new data-race candidate entirely, %in some alternate interleaving,
in which case we iteratively advance to a superset state space containing PPs for both racing access pairs.
%Because Iterative Deepening is
Being constrained by a CPU budget,
we may time out before completing a data race's associated state space,
in which case it remains a potential false positive that the user must handle.

### 2015-11-18 pldi-16/implementation.tex
implement brandon's comments, and trim a bit; back onto 12th page, oops

We chose \landslide~\cite{landslide} as our stateless model checker due to its ability to trace program execution at the granularity of individual instructions and memory accesses, which dynamic data-race detection requires.
\landslide~implements DPOR \cite{dpor},
%\cite{dpor},
state space estimation \cite{estimation}, and a hybrid lockset/happens-before data-race analysis \cite{hybriddatarace}.
It avoids state space cycles (e.g. ad-hoc synchronization with {\tt yield} or even {\tt xchg} loops) with a heuristic similar to Fair-Bounded Search \cite{bpor}.
% this line can be cut if space is needed
%It can test both user-level and kernel-level code, although is limited to timer-driven nondeterminism.
% joshua wants "segfault" to be "memory access error (i.e., segmentation fault, or bus error)"
Its bug-detection metrics include assertion failure, deadlock, segfault, heap checking (like Valgrind~\cite{valgrind}), and a heuristic infinite loop/livelock check.

>>>>

We chose \landslide~\cite{landslide} as our stateless model checker due to its ability to trace program execution at the granularity of individual instructions and memory accesses, which dynamic data-race detection requires.
\landslide~implements DPOR \cite{dpor},
%\cite{dpor},
state space estimation \cite{estimation}, and a hybrid lockset/happens-before data-race analysis \cite{hybriddatarace}.
It avoids state space cycles (e.g. ad-hoc synchronization with {\tt yield} or even {\tt xchg} loops) with a heuristic similar to Fair-Bounded Search \cite{bpor}.
% this line can be cut if space is needed
It can test both user-level and kernel-level code, although is limited to timer nondeterminism.
% joshua wants "segfault" to be "memory access error (i.e., segmentation fault, or bus error)"
Its bug-detection metrics are assertion failure, deadlock, segfault, heap checking \cite{valgrind}, and a heuristic infinite loop check.

### 2015-11-18 pldi-16/intro.tex
trim some lines
implement brandon's comments, and trim a bit; back onto 12th page, oops

% Can I even make a claim this broad to begin with?
However, all stateless model checkers to date are bound by a fixed set of {\em preemption points}: code locations that define the granularity at which threads interleave.
Choosing these preemption points is a tradeoff between schedule coverage and feasibility of completion.
For example, \textsc{CHESS} \cite{chess} preempts only on synchronization operations and library calls, which can miss lock-free shared memory races.
%
On the other hand, Inspect \cite{inspect} %SPIN \cite{spin}
is able to preempt threads around any shared memory access. Such fine granularity would automatically check if each data race is a real bug, but makes full state space completion intractable for even modestly-sized tests.
%
This work shows how to avoid making that tradeoff decision in advance.

@@

The remainder of the paper is organized as follows.
\sect{\ref{sec:overview}} reviews the background material, %on stateless model checking and data-race analysis,
\sect{\ref{sec:design}} and \sect{\ref{sec:implementation}} discuss our design and implementation, %of Iterative Deepening,
\sect{\ref{sec:soundness}} presents our proofs of convergence and of the soundness of our new false-positive data-race tactic,
\sect{\ref{sec:eval}} presents our evaluation,
\sect{\ref{sec:future}} discusses limitations and future work,
\sect{\ref{sec:related}} surveys the related work,
and \sect{\ref{sec:conclusion}} concludes.

>>>>

% Can I even make a claim this broad to begin with?
However, all stateless model checkers to date are bound by a fixed set of {\em preemption points}: code locations that define the granularity at which threads interleave.
Choosing these preemption points is a tradeoff between schedule coverage and feasibility of completion.
For example, \textsc{CHESS} \cite{chess} preempts only on synchronization operations and library calls, which can miss lock-free shared memory races.
%
On the other hand, SPIN \cite{spin} and Inspect \cite{inspect}
are able to preempt threads around any shared memory access. Such fine granularity would automatically check if each data race is a real bug, but makes full state space completion intractable for even modestly-sized tests.
%
This work shows how to avoid making that tradeoff decision in advance.

@@

The rest of the paper is organized as follows.
\sect{\ref{sec:overview}} reviews the background material, %on stateless model checking and data-race analysis,
\sect{\ref{sec:design}} and \sect{\ref{sec:implementation}} discuss our design and implementation, %of Iterative Deepening,
\sect{\ref{sec:soundness}} presents our proofs of convergence and of the soundness of our new false-positive data-race tactic,
\sect{\ref{sec:eval}} presents our evaluation,
\sect{\ref{sec:future}} discusses limitations and future work,
\sect{\ref{sec:related}} surveys the related work,
and \sect{\ref{sec:conclusion}} concludes.

### 2015-11-18 pldi-16/overview.tex
TRIMTRIMTRIM. back on 11 pages woo!
Finish the table. Paper can now be called 100% complete, in a pinch.
implement brandon's comments, and trim a bit; back onto 12th page, oops

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{trees-v2.pdf}
	\caption{Iterative Deepening example.
		The minimal state space (top) includes only voluntary thread switches, such as {\tt yield()}. %or {\tt cond\_wait()}.
		Multiple further tests can be run: preempting on calls to {\tt mutex\_lock} alone (left), {\tt mutex\_unlock} alone (right), or both together (bottom).
Each option increases the state space size unpredictably, so multiple state spaces should be tested in parallel.
Estimation techniques~\cite{estimation} inform which state spaces to prioritize.
}
	\label{fig:id}
\end{figure}

The checker defins the granularity of thread interleavings by which {\em preemption points} it uses to switch threads.
Most model checkers \cite{chess} choose synchronization/thread library API boundaries for these points;
in our example program, these would be lines 1, 4, and 7.
Figure~\ref{fig:id} shows several possible resulting state spaces.
The approach of prior work is to enable all preemption points simultaneously, i.e., to test only the bottom state space.

@@

This motivates {\em Iterative Deepening}, our new technique for adjusting the preemption points at runtime.
Rather than committing to one state space with every available preemption point enabled,
Iterative Deepening searches among different {\em subsets} of the points;
for example, ``preempt on all calls to {\tt mutex\_lock} but not on {\tt mutex\_unlock}''.
Hence, we will test all the state spaces shown in Figure~\ref{fig:id} in parallel,
and decide on-the-fly whether to pursue each test, or to defer it in favour of smaller ones.

@@

@@

SSS-MC indicates the approach of prior model checking tools:
the set of PPs is fixed in advance, and the tool commits to testing every interleaving available with those PPs.
%Reduction techniques are often used to skip equivalent interleavings \cite{dpor}, and search-ordering strategies
Many techniques exist to skip equivalent interleavings and order the search to uncover bugs faster \cite{dpor,demeter,chess-icb,gambit},
but new PPs cannot be added, nor ineffective ones removed, by any dynamic analysis.

We distinguish between data-race {\em candidates} and data-race {\em bugs}.
Because data-race analysis is prone to false-positives,
we classify unprotected access pairs separately from bugs,
calling such pairs {\em data race candidates}.
Should a future interleaving, preempting during those accesses,
lead to a failure, then we report a {\em data-race bug}.
Otherwise, if the access pair can be reordered, but does not produce a failure under any interleaving, it is a {\em benign data race}.
If they cannot be reordered at all, it is a {\em false positive}.
%TODO: Don't do this, below. Scan paper for uses of 'false positive' where you mean to say 'benign' or 'both'.
%For brevity, we count benign data races as a subset of false positives.

>>>>

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{trees-v2-squashed.pdf}
	\caption{Iterative Deepening example.
		The minimal state space (top) includes only voluntary thread switches, such as {\tt yield()}. %or {\tt cond\_wait()}.
		Multiple further tests can be run: preempting on calls to {\tt mutex\_lock} alone (left), {\tt mutex\_unlock} alone (right), or both together (bottom).
Each option increases the state space size unpredictably, so multiple state spaces should be tested in parallel.
Estimation techniques~\cite{estimation} inform which state spaces to prioritize.
}
	\label{fig:id}
\end{figure}

The checker defins the granularity of thread interleavings by which {\em preemption points} it uses to switch threads.
Most model checkers \cite{chess,dbug-ssv} choose synchronization/thread library API boundaries for these points;
in our example program, these would be lines 1, 4, and 7.
Figure~\ref{fig:id} shows several possible resulting state spaces.
The approach of prior work is to enable all preemption points simultaneously, i.e., to test only the bottom state space.

@@

This motivates {\em Iterative Deepening}, our new technique for heuristically adjusting the preemption points at runtime.
Rather than committing to one state space with every available preemption point enabled,
Iterative Deepening searches among different {\em subsets} of the points;
for example, ``preempt on all calls to {\tt mutex\_lock} but not on {\tt mutex\_unlock}''.
Hence, we will test all the state spaces shown in Figure~\ref{fig:id} in parallel,
and decide on-the-fly whether to pursue each test, or to defer it in favour of smaller ones.

@@

Prior work \cite{hybriddatarace} distinguishes between {\em pure happens-before} \cite{lamport-clocks},
in which accesses with a lock release/acquire in between are not considered concurrent,
and {\em limited happens-before},
in which only blocking operations like {\tt cond\_wait} or {\tt join} enforce the order.
Compared to the former, the latter may output false positives, but avoids false negatives \cite{tsan},
which is more appropriate for this work (\sect{\ref{sec:totalverif}}).

@@

SSS-MC indicates the approach of prior model checking tools:
the set of PPs is fixed in advance, and the tool commits to testing every interleaving available with those PPs.
%Reduction techniques are often used to skip equivalent interleavings \cite{dpor}, and search-ordering strategies
Many techniques exist to skip equivalent interleavings and order the search to uncover bugs faster \cite{dpor,demeter,chess-icb,gambit,smc-empirical-study},
but new PPs cannot be added, nor ineffective ones removed, by any dynamic analysis.

Although all data races are undefined behaviour in C and C++ \cite{boehm-memorymodels},
we distinguish between data-race {\em candidates} and data-race {\em bugs}.
Because data-race analysis is prone to false-positives,
we classify unprotected access pairs separately from bugs,
calling such pairs {\em data race candidates}.
Should a future interleaving, preempting during those accesses,
lead to a failure, then we report a {\em data-race bug}.
Otherwise, if the access pair can be reordered, but does not produce a failure under any interleaving, it is a {\em benign data race}.
If they cannot be reordered at all, it is a {\em false positive}.
%TODO: Don't do this, below. Scan paper for uses of 'false positive' where you mean to say 'benign' or 'both'.
%For brevity, we count benign data races as a subset of false positives.

### 2015-11-18 pldi-16/paper.tex
implement brandon's comments, and trim a bit; back onto 12th page, oops

%Although \landslide~itself is not publicly available due to its dependency on the non-free simulator \simics, \quicksand~is open-source and its interface can be adapted to fit any similar tool.
\quicksand~is open-source and its interface can be adapted to fit any MC tool similar to \landslide.
We have also posted our evaluation's full data set and logs.
They can be found here:

@@

\section{Acknowledgements}

% TODO CAMREADY
{\em removed for double-blind review}
%Many thanks to Vaishaal Shankar, Haryadi Gunawi, and David A. Eckhardt for generously providing student implementations from Berkeley's, U. of Chicago's, and CMU's OS classes respectively.
%Thanks to Wind River for the use of their simulator \simics.
%Thanks to
%Ji\v{r}\'{i} \v{S}im\v{s}a, Joshua Wise, John Wilkes, and
%the anonymous PLDI reviewers for their helpful comments.
%This work was supported in part by
%the U.S. Army Research Office under grant number W911NF0910273.

>>>>

%Although \landslide~itself is not publicly available due to its dependency on the non-free simulator \simics, \quicksand~is open-source and its interface can be adapted to fit any similar tool.
\quicksand~is open-source and its interface can be adapted to fit any tool similar to \landslide.
We have also posted our evaluation's full data set. %and logs.
They are available at:

@@

%\section{Acknowledgements}

% TODO CAMREADY
%{\em removed for double-blind review}
%Many thanks to Vaishaal Shankar, Haryadi Gunawi, and David A. Eckhardt for generously providing student implementations from Berkeley's, U. of Chicago's, and CMU's OS classes respectively.
%Thanks to Wind River for the use of their simulator \simics.
%Thanks to
%Ji\v{r}\'{i} \v{S}im\v{s}a, Joshua Wise, Jean Yang, Brandon Lucia, John Wilkes, and
%the anonymous PLDI reviewers for their helpful comments.
%This work was supported in part by
%the U.S. Army Research Office under grant number W911NF0910273.

### 2015-11-18 pldi-16/related.tex
implement brandon's comments, and trim a bit; back onto 12th page, oops

{\bf Other techniques.} Various improvements to DPOR have been proposed, such as Dynamic Interface Reduction \cite{demeter}, Maximal Causality Reduction \cite{mcr}, and DPOR for TSO/PSO \cite{tsopso}.
These are all orthogonal to our technique.
Parrot \cite{parrot} combines MC with a partially-determinizing runtime, but still, fewer than half the non-trivial state spaces in their evaluation could be completed.
%providing a strong argument for \quicksand.
Finally, Iterative Context Bounding (ICB) \cite{chess-icb} is most similar to Iterative Deepening,
as both approaches provide a partial verification on some subset of interleavings when full completion is intractable (\sect{\ref{sec:future}}).
However, ICB is limited to a fixed set of PPs, and so far no algorithm has been proposed to dynamically add data-race PPs during a test with ICB.

@@

%Too many related projects to list have made contributions to the
Many advances have been made on the false-positive data race problem since it was first introduced in \cite{eraser}.
\cite{hybriddatarace} and \cite{tsan} combine the lockset and happens-before analyses into a hybrid technique, which we employ.
% TODO: any more?
DroidRacer \cite{droidracer} and CAFA \cite{cafa} extend the analysis to event-driven Android applications, using domain-specific heuristics (orthogonal to our method) to reduce false positives. % cut for space?
% No, IDGAF about pure happens before.
%FastTrack \cite{fasttrack} optimizes the performance of pure happens-

@@

Portend \cite{portend} is the most closely related work we have found.
Based on single-pass data race reports, it tests alternate program executions to classify candidates in a taxonomy of likely severity.
It uses symbolic execution to test input nondeterminism as well as schedule nondeterminism,
while we explore the latter only.
Portend additionally reports non-failing races which nevertheless cause
%suspiciously
different program output, which is orthogonal to our technique.
However, Portend does not test alternate interleavings {\em in advance} of knowing data races,
which is necessary to expose certain bugs (\sect{\ref{sec:eval-falseneg}}) or to provide full verification (\sect{\ref{sec:totalverif}}).
% XXX: Is this true??
%It also assumes the POSIX synchronization API, so cannot verify arbitrary synchronization algorithms such as we do with \mxtest.
Future work could combine the two approaches, using MC to produce new data-race traces for Portend to classify, or using Portend's analysis to inform \quicksand's heuristic priorities.

>>>>

{\bf Other techniques.} Various improvements or alternatives to DPOR have been proposed, such as Dynamic Interface Reduction \cite{demeter}, Maximal Causality Reduction \cite{mcr}, DPOR for relaxed memory models \cite{tsopso}, and SAT-directed MC \cite{satcheck}.
These are all orthogonal to our technique.
Parrot \cite{parrot} combines MC with a partially-determinizing runtime, but still, fewer than half the non-trivial state spaces in their evaluation could be completed.
%providing a strong argument for \quicksand.
Finally, Iterative Context Bounding (ICB) \cite{chess-icb} is most similar to our work,
as both approaches provide a partial verification
%on some subset of interleavings
when full completion is intractable (\sect{\ref{sec:future}}).
However, ICB is limited to a fixed set of PPs, and so far no algorithm has been proposed to dynamically add data-race PPs during a test with ICB.

@@

%Too many related projects to list have made contributions to the
Many advances have been made on the false-positive data race problem since it was first introduced in \cite{eraser}.
\cite{hybriddatarace} and \cite{tsan} combine the lockset and happens-before analyses into a hybrid technique, which we employ.
DroidRacer \cite{droidracer} and CAFA \cite{cafa} target
%event-driven
Android applications, using domain-specific heuristics (orthogonal to our method) to reduce false positives. % cut for space?
Like \landslide, DataCollider \cite{datacollider} offers data-race techniques for kernel code.
IFRit \cite{ifrit}
improves performance using an interference analysis,
which would allow future work to avoid tracing every memory access.
%although in our context, we cannot admit false negatives (\sect{\ref{sec:totalverif}}).
% No, IDGAF about pure happens before.
%FastTrack \cite{fasttrack} optimizes the performance of pure happens-

@@

Portend \cite{portend} is the most closely related work we have found.
Based on single-pass data race reports, it tests alternate program executions to classify candidates in a taxonomy of likely severity.
It uses symbolic execution to test input nondeterminism as well as schedule nondeterminism,
%while we explore the latter only.
and additionally reports non-failing races which nevertheless cause
%suspiciously
different program output. %, which is orthogonal to our technique.
However, Portend does not test alternate interleavings {\em in advance} of knowing data races,
which is necessary to expose certain bugs (\sect{\ref{sec:eval-falseneg}}) or to provide full verification (\sect{\ref{sec:totalverif}}).
% Not really true.
%It also assumes the POSIX synchronization API, so cannot verify arbitrary synchronization algorithms such as we do with \mxtest.
Future work could combine the two approaches, using MC to produce new data-race traces for Portend to classify, or using Portend's analysis to inform \quicksand's heuristic priorities.

### 2015-11-18 pldi-16/soundness.tex
implement brandon's comments, and trim a bit; back onto 12th page, oops

\begin{figure}[t]
	\small
\begin{tabular}{rll}
	& \multicolumn{2}{c}{\texttt{struct x \{ int foo; int baz; \} *x;}} \\
	& \multicolumn{2}{c}{\texttt{struct y \{ int bar; \} *y;~~~~~~~~~~}} \\
	& {\bf Thread 1} & {\bf Thread 2} \\
	1 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
	2 & \texttt{\hilight{olivegreen}{free}(x);} \\
	3 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
	4 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
	5 & & \texttt{\hilight{commentblue}{// ...initialize...}}\\
	6 & & \texttt{publish(y);} \\
	7 & & \texttt{\hilight{brickred}{y->bar = ...;}} \\
\end{tabular}
\caption{A common execution pattern with {\tt malloc()} that produces false positive data race candidates.}
\label{fig:recycle}
\end{figure}
\begin{figure}[t]
	\small
\begin{tabular}{rll}
	& {\bf Thread 1} & {\bf Thread 2} \\
	1 & \texttt{publish(x);} & \\
	2 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
	3 & \texttt{\hilight{olivegreen}{free}(x);} \\
	4 & & \texttt{x2 = get\_published\_x();} \\
	5 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
	6 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
	7 & & \texttt{\hilight{brickred}{x2->foo = ...;}} \\
\end{tabular}
\caption{If a single-pass data race detector discarded candidates matching the malloc-recycle pattern,
it would miss the bug in this adversarial program.}
\label{fig:recycle-bug}
\end{figure}

>>>>

\begin{figure}[t]
	\small
\begin{tabular}{rll}
	%& \multicolumn{2}{c}{\texttt{struct x \{ int foo; int baz; \} *x;}} \\
	%& \multicolumn{2}{c}{\texttt{struct y \{ int bar; \} *y;~~~~~~~~~~}} \\
	& {\bf Thread 1} & {\bf Thread 2} \\
	1 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
	2 & \texttt{\hilight{olivegreen}{free}(x);} \\
	3 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
	4 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
	5 & & \texttt{\hilight{commentblue}{// ...initialize...}}\\
	6 & & \texttt{publish(y);} \\
	7 & & \texttt{\hilight{brickred}{y->bar = ...;}} \\
\end{tabular}
\caption{A common execution pattern with {\tt malloc()} that produces false positive data race candidates.}
\label{fig:recycle}
\end{figure}
\begin{figure}[t]
	\small
\begin{tabular}{rll}
	& {\bf Thread 1} & {\bf Thread 2} \\
	1 & \texttt{publish(x);} & \\
	2 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
	3 & \texttt{\hilight{olivegreen}{free}(x);} \\
	4 & & \texttt{x2 = get\_published\_x();} \\
	5 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
	6 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
	7 & & \texttt{\hilight{brickred}{x2->foo = ...;}} \\
\end{tabular}
\caption{If a single-pass data race detector discarded candidates matching the malloc-recycle pattern,
it would miss the bug in this adversarial program.}
\label{fig:recycle-bug}
\end{figure}

### 2015-11-18 pldi-16/testcases/testcases.tex
implement brandon's comments, and trim a bit; back onto 12th page, oops

\maketitle
\begin{abstract}
In our paper we show the effectiveness of combining dynamic data-race detection \cite{eraser,hybriddatarace} with stateless model checking \cite{verisoft,dpor}.
Our approach involves adding new state spaces to explore each time a new data-race candidate is found.
This document presents the source code of the 9 test cases we used, as supplemental material to our main paper.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
In our paper we show the effectiveness of combining dynamic data-race detection \cite{eraser,hybriddatarace} with stateless model checking \cite{verisoft,dpor,chess}.
Our approach involves adding new state spaces to explore each time a new data-race candidate is found.
This document presents the source code of the 9 test cases we used, as supplemental material to our main paper.
\end{abstract}
